Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2017-06-05 paper/submitted/reviews/reviewer_response.tex

On page 8 (before equation 10), the sentence “Note that, ..” references equation 11 before it is
presented. It may be better to move this comment to immediately follow the description of equation
11.

\answer{blah}
\notdone

I found the motivation in the beginning of the manuscript somewhat lacking. The description of use
cases, and conditions for which the algorithm is suitable, from the last paragraph on page 9 were very
helpful. I believe the presentation would be strengthened by mentioning some of this earlier in the
introduction.

\answer{We added a sentence about the use cases to the second paragraph of the introduction.}

@@

Although it is represented graphically in Figure 8, $\Omega_I$ for the final example is not defined in the text.

\answer{It is now defined just before Figure 8 is referenced.}

@@

At the beginning of the second paragraph of Section 4.3.2 (pg. 25) I think the reference to “Section
4.3.2” should be Table 1.

\answer{Thanks for the catch. We've corrected the reference.}

The sub-figures of Figure 9 could be larger. It is difficult to verify the claim in the text that “. . . the
domain is refined completely in the $x_3$ direction first around the QoI region. . . ”. Even going as far as
to include 2-D slices (as in Figure 8) may be warranted.

\answer{We made the figure larger, made the wording of that claim more specific, and included a 2D slice for each mixed-fidelity model that cuts through the QoI region, to aid in visual verification.}

@@

The second to last paragraph on page 28 starts “Section 4.3.2 shows the average QoI. . . ”. Again, I
believe this is a reference to a table, Table 2 in this case.

\answer{Thanks for the catch. We've corrected the reference.}

@@

It could be illustrative to see how the parameters q change with the refinement process.

\answer{}
\notdone

Figure 3 is not particularly illustrative, especially on linear scale. Perhaps some tuning of the
refinement parameters? What were the refinement parameters for the examples?

\answer{Modified figures to be on log scale and include line for target QoI error, and removed 100\% refinement point, since we don't keep refining after target is reached...not sure what is meant by 'refinement parameters'...Figure 3 was only meant to show that error decreased with refinement and that only two iterations were necessary...the amount to refine in each iteration is arbitrarily/chosen-by-used...}
\notdone

### 2017-06-05 paper/submitted/round2_png/algorithms_v4_cmame.tex
more paper changes

>>>>

%%%% FIX BELOW ONCE YOU HAVE NOTATION DOWN FOR SECTION 2

We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements. For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$. Note that the error estimate in \cref{eq:finErrExp} can be equivalently written as,
%
\begin{equation}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
\end{equation}
%
We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$. Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum\limits_{i\in I}\varphi_i\lambda_i,\sum\limits_{i\in I}\upvarphi_i \chi_i)$. The error estimate,
%
\begin{equation}
\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
\end{equation}
%
where,
%
\begin{equation}\label{eq:basisblame}
\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
\end{equation}
%
can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$. Near the interfaces between the low-fidelity and high-fidelity regions, basis functions may have their support divided between the two regions and thus have a nonzero error contribution. The basis functions with the largest error contributions are flagged, and the elements in their support are refined.

### 2017-06-05 paper/submitted/round2_png/numerical_experiments_v4_cmame.tex
more paper changes

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...}
The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable. The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.

@@

\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \Cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively. In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that while here the error is seen to decrease with increasing refinement, in general there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}
%

@@

\Cref{fig:qoiStudy} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
The error decompositions for each case are also shown in \Cref{fig:qoiStudy}. The bottom row gives the baseline case presented in \Cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \Cref{sec:cdvcdrBaseRef}.
% KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
Although refinement is still most important around the observation location closest to $x_1=0$, as the QoI region expands the other two observation locations become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
  \label{subfig:obsSetup}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
  \label{subfig:obsLF}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:qoiStudy}
\end{figure}

\Cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
The error decomposition for the three cases is shown in \Cref{fig:dataStudy}. The bottom row is the same as that in \Cref{fig:qoiStudy}. Refinement appears to be consistently most important around the observation location closest to $x_1=0$ and the QoI region. However, as more observation locations are added, it becomes no longer necessarily true that refinement becomes less important around observation locations as their distance from the QoI region increases. In the second and third rows, one can see that after the areas around the QoI region and the two closest observation locations have been refined, the next area to be refined is not around the third closest observation location, but rather around one near the middle of the domain. This suggests that interactions between observation locations and the QoI may be non-intuitive, and in these cases a rigorous method for forming a mixed-fidelity model leads to well-supported modeling choices.

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
  \includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
  \label{subfig:obsSetup2}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
  \label{subfig:obsLF2}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
  \label{subfig:obsMFlast2}
}
  \caption{Effects of increasing the number of observations. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:dataStudy}
\end{figure}

@@

We consider the same high-fidelity model as in \Cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field. The intermediate mixed-fidelity models thus have parameter fields that are constant over the subregions of the domain where the low-fidelity model is used. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \Cref{sec:cdvcdr}. As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.

@@

The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain. We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.

@@

The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$. Synthetic observations at 18 points in the domain are generated by running the high-fidelity model on a finer mesh. The locations of the observations as well as the QoI region $\Omega_I$ are shown in \Cref{fig:setup3D}. We set the regularization term in \Cref{eq:invOpt_obj} to be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.4\textwidth]{series3D/setup_aerial_nolegend.pdf} \hfill
\includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\
\vspace{\baselineskip}
\includegraphics[width=0.6\textwidth]{series3D/setup_side_view.pdf}
\caption{Three views of the locations of the observations and the QoI region.}
\label{fig:setup3D}
\end{figure}
%

@@

The multi-fidelity domain refinements for the five adaptive iterations are shown in \Cref{fig:divvy3D_diffmesh}. Similarly to the behavior seen in \Cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to receive refinement. We also see that the domain is refined completely in the $x_3$ direction first around the QoI region, reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
%
\begin{figure}[htbp]
\centering
\subfloat[Slice location]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/slice_diagram.png}
}
\hfill
\subfloat[MF$_1$ ($5.2\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff_and_midslice.png}
}
\\
\subfloat[MF$_2$ ($11.4\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff_and_midslice.png}
} 
\hfill
\subfloat[MF$_3$ ($16.3\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff_and_midslice.png}
} \\
\subfloat[MF$_4$ ($22.0\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff_and_midslice.png}
} 
\hfill
\subfloat[MF$_5$ ($27.7\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff_and_midslice.png}
}

\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
\label{fig:divvy3D_diffmesh}
\end{figure}
%

>>>>

For the numerical simulations, we use the finite element method (FEM), employing a continuous Galerkin formulation with linear Lagrange elements. We use the \texttt{libMesh} library~\cite{libMeshPaper} for the FEM calculations.
%\red{The library offers easy calculation of adjoint systems, error estimates and subdomain restricted variables.}\footnote{But we don't use Libmesh's error estimates or restrict variables to subdomains...}
The domain is discretized by a regular mesh of quadrilaterals, with 250 and 50 elements along the $x_1$ and $x_2$ directions, respectively, for a total of 12,500 elements, resulting in 12,801 degrees of freedom per variable; all variables are represented by the same basis. The diffusion coefficient is such that the cell P\'{e}clet number never exceeds 0.1, and thus no stabilization is required.

@@

\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \Cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively. In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that while here the error is seen to decrease with increasing refinement, in general there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\includegraphics[width=0.8\textwidth]{baseSeries/err_est_v2.pdf}
%\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used. In this case, only two refinement iterations are necessary to achieve the target relative QoI error (dotted line).}
\label{fig:baseErr}
\end{figure}
%

@@

\Cref{subfig:obsSetup} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
The error decompositions for each case are shown in \Cref{subfig:obsLF,subfig:obsMF1,subfig:obsMFlast}. The bottom row gives the baseline case presented in \Cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \Cref{sec:cdvcdrBaseRef}.
% KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
Although refinement is still most important around the observation location closest to $x_1=0$, as the QoI region expands the other two observation locations become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
  \label{subfig:obsSetup}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
  \label{subfig:obsLF}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
  \label{subfig:obsMF1}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:qoiStudy}
\end{figure}

\Cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
The error decomposition for the three cases is shown in \Cref{subfig:obsLF2,subfig:obsMF1_2,subfig:obsMFlast2}. The bottom row is the same as that in \Cref{fig:qoiStudy}. Refinement appears to be consistently most important around the observation location closest to $x_1=0$ and the QoI region. However, as more observation locations are added, it becomes no longer necessarily true that refinement becomes less important around observation locations as their distance from the QoI region increases. In the second and third rows, one can see that after the areas around the QoI region and the two closest observation locations have been refined, the next area to be refined is not around the third closest observation location, but rather around one near the middle of the domain. This suggests that interactions between observation locations and the QoI may be non-intuitive, and in these cases a rigorous method for forming a mixed-fidelity model leads to well-supported modeling choices.

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_setup.png}
  \includegraphics[width=0.21\textwidth]{vs_data/vs_data_setup_sidetrim.png}
  \label{subfig:obsSetup2}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err0.png}
  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err0_nobar.png}
  \label{subfig:obsLF2}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err1.png}
  \includegraphics[width=0.16\textwidth]{vs_data/vs_data_err1_nobar.png}
  \label{subfig:obsMF1_2}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2.png}
  \includegraphics[width=0.23\textwidth]{vs_data/vs_data_err2_barnorm.png}
  \label{subfig:obsMFlast2}
}
  \caption{Effects of increasing the number of observations. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}: the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:dataStudy}
\end{figure}

@@

We consider the same high-fidelity model as in \Cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field; $f(q)$ is a constant function equal to $q$ everywhere in the domain. The intermediate mixed-fidelity models thus have parameter fields (and forcing functions) that are constant over the subregions of the domain where the low-fidelity model is used; disconnected low-fidelity regions still share the same parameter value. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The domain, mesh, boundary conditions, and velocity field, as well as the observations and QoI, remain the same as described in \Cref{sec:cdvcdr}; we continue to infer for the forcing field. The forcing field (and its auxiliary and supplementary adjoint conterparts) are represented with the same basis functions as the other variables in the high-fidelity regions, and forced to be constant in the low-fidelity regions. As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.

@@

The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\includegraphics[width=0.8\textwidth]{svf/err_est_v2.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used. The dotted line indicates the target relative QoI error.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain. We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.

@@

The unknown parameters we wish to infer correspond to the source term $f(q)=q$; we impose $f(q)=q=0$ on the boundary $\partial\Omega$. Synthetic observations at 18 points in the domain are generated by running the high-fidelity model on a finer mesh. The locations of the observations as well as the QoI region $\Omega_I=[1100\textrm{m},1200\textrm{m}]\times[775\textrm{m},875\textrm{m}]\times[80\textrm{m},100\textrm{m}]$ are shown in \Cref{fig:setup3D}. We set the regularization term in \Cref{eq:invOpt_obj} to be $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}V$.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.4\textwidth]{series3D/setup_aerial_nolegend.pdf} \hfill
\includegraphics[width=0.55\textwidth]{series3D/setup_3view.pdf} \\
\vspace{\baselineskip}
\includegraphics[width=0.6\textwidth]{series3D/setup_side_view.pdf}
\caption{Three views of the locations of the observations and the QoI region.}
\label{fig:setup3D}
\end{figure}
%

@@

The multi-fidelity domain refinements for the five adaptive iterations are shown in \Cref{fig:divvy3D_diffmesh}. Similarly to the behavior seen in \Cref{sec:cdvcdrBaseRef}, the QoI region and the areas around some of the measurement points are first targeted for refinement, with those measurement points furthest downstream of the QoI being the last to receive refinement. We also see that the domain is refined completely in the $x_3$ direction first in an area slightly upstream of the QoI region (see \Cref{subfig:3DMF2}), reflecting the large difference in the high-fidelity dispersion tensor $D$ and the low-fidelity dispersion coefficient in the $x_3$ direction.
%
\begin{figure}[htbp]
\centering
\subfloat[Slice location and color key]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/slice_diagram.png}
\label{subfig:3Dsliceloc}
}
\hfill
\subfloat[MF$_1$ ($5.2\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy1_whitebg_puff_and_midslice.png}
\label{subfig:3DMF1}
}
\\
\subfloat[MF$_2$ ($11.4\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy2_whitebg_puff_and_midslice.png}
\label{subfig:3DMF2}
} 
\hfill
\subfloat[MF$_3$ ($16.3\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy3_whitebg_puff_and_midslice.png}
} \\
\subfloat[MF$_4$ ($22.0\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy4_whitebg_puff_and_midslice.png}
} 
\hfill
\subfloat[MF$_5$ ($27.7\%$ HF)]{
\includegraphics[width=0.42\textwidth]{series3D/run_diff_mesh/divvy5_whitebg_puff_and_midslice.png}
\label{subfig:3Dfinref}
}

\caption{Domain division for mixed-fidelity models (\protect\subref{subfig:3DMF1}--\protect\subref{subfig:3Dfinref}): 3D view with 2D slice through domain below (see \protect\subref{subfig:3Dsliceloc} for slice location and orientation). Low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors in 3D view due to transparency indicate a mix of the two models along the line of sight). Slices cut through QoI region, indicated by purple box. $x_3$ direction scaled for clarity.}
\label{fig:divvy3D_diffmesh}
\end{figure}
%
